Inventory management is an important part of running business and managing items around us.  Traditional practice of managing items for business cost a lot of time and work force for companies.  Customers become frustrated when the items they're looking for aren't available on the shelf. Bad practice of managing items in our home, school, works etc. cost lots of time because it is hard for us to remember what items are needed and where it is located. Pocket-self is the inventory tracking ISO/Android based mobile application which allow users to keep the items in available space, which is created by the user.We called PocketShelf because the idea behind it, we can carry the inventory application in our pocket and can search items in just a click. The function of the app is user can sign up and login then add items or add shelf or search the items.App can help to find the place where to keep the items in shelf, keeps record of it and help to find the items when customers search for it.  The app can help the customers to find and add the items in the shelf with the help of the items pictures too.  We used Augmented reality as our key feature of the application.  Where user can see the item before they approach to grab it.  Which might be helpful in the sense that it will save the user effort and time spent and they know that they are getting the right thing. Time frame to notify user can be predefined by the user at the time of its entry. Our app use the online database to save every entry by the user and had to be encrypted before it goes to the database,all the data had to flow through the server.  So, user must be online to be able to use the app.  We had PIN protection as an extra feature on the app, where if the user wants not to show the item location to another user using the same app on same device.  Which we found cool feature if the user wants to secure valuable items somewhere in the shelf.The scope of pocketShelf are prioritize inventory, Track all product information, Track sales, sorts in-venture according to manufacture and best by date of the items.  App helps to prioritize inventory on the basic of the customers demand, shape and sizes of items in the shelf.  For example, heavy and big items are preferred in he button of the shelf and small or light items in the top the shelf. App will keep the records of the inventory as well as items in stocks.  Another important feature of the app is track sales.  Update the numbers of the items when add or remove an item from the shelf.  App can sort the inventory according to customer preferences based on attributes of the item.  The app not only keep track of the item but able to sort the items based on the expiration dates and can notify the user if the item is expiring soon.